---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# minvariance

<!-- badges: start -->
<!-- badges: end -->

The goal of `minvariance` is to help me understand longitudinal measurement invariance.
I'm trying to see which parts of this method can be automated.
The vignettes on the [website](https://milanwiedemann.github.io/minvariance/) of this package replicate some example I found online.
**If you have any questions, ideas, or comments please get in touch.**

## Installation

You can install the released version of `minvariance` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("milanwiedemann/minvariance")
```

```{r}
library(tidyverse)
library(minvariance)

# Specify list of variables 
# Generate lavaan syntax
long_minvariance_syntax(var_list = list(t1 = c("i1_t1", "i2_t1", "i3_t1"), 
                                        t2 = c("i1_t2", "i1_t2", "i1_t2")), 
                        model = "configural") %>% 
  cat()
```

Here's another example with different variable names

```{r}
library(tidyverse)

# Generate lavaan syntax
long_minvariance_syntax(var_list = list(t1 = c("a1", "b1", "c1"), 
                                        t2 = c("a2", "b2", "c2")), 
                        model = "strong") %>% 
  cat()

```



## Resources and related work 

R functions to test for longitudinal factorial/measurement invariance 

- [Longitudinal Factor Analysis - Measurement Invariance by Nilam Ram](https://quantdev.ssri.psu.edu/tutorials/intro-basics-longitudinal-measurement-invariance)
- [Measurement Matters Resource List by Eiko Fried and Jessica Flake](https://docs.google.com/document/d/11jyoXtO0m2lUywpC04KjLvI5QcBUY4YtwEvw6cg2cMs)
- [Fried et al (2016). Measuring depression over time . . . Or not? Lack of unidimensionality and longitudinal measurement invariance in four common rating scales of depression. Psychological Assessment.](https://doi.org/10.1037/pas0000275) and [Supplemental Materials](http://supp.apa.org/psycarticles/supplemental/pas0000275/supplementary_materials.zip) with Mplus files
- [Grimm (2017) - lavaan Code for Chapter 14 - Modeling Change with Latent Variables Measured by Continuous Indicators by Julie Wood](https://quantdev.ssri.psu.edu/tutorials/growth-modeling-chapter-14-modeling-change-latent-variables-measured-continuous-indicators)
- [MIE - Measurement invariance explorer (R package) by Maksim Rudnev](https://github.com/MaksimRudnev/MIE.package)
- ["A Tutorial in Longitudinal Measurement Invariance Using Lavaan" by Robin Curtis, Sean Mackinnon, Roisin O'Connor](https://psyarxiv.com/tkzrb/)
- [measEq.syntax {semTools}](https://www.rdocumentation.org/packages/semTools/versions/0.5-2/topics/measEq.syntax)
- [On dimensionality, measurement invariance and suitabilityof sum scores for the PHQ-9 and the GAD-7](https://osf.io/arufy/) with Mplus Code using mplusautomation
- [lavaan group](https://groups.google.com/forum/#!topic/lavaan/nfdatPgLLhc)

